Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-15 TitlePage.tex
Make titlepage closer to university example
Refactor titlepage to be simpler and more robust
By using a global \large, we don't need to ensure that paragraphs end in scope
of `\large` declarations with \par.

Also other misc simplifications.

And move all title-page related boilerplate from thesis-main.tex.

\begin{center}

\vspace{2cm}

\makeatletter
{\huge \bfseries \@title}\\

\vspace{5cm}

{\Large \bfseries Dissertation}\\

\vspace{0.5cm}

{\large der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)}\\

\vspace{5 cm}

{\large vorgelegt von \\
\@author\\
aus Catania (Italien)}\\

\vspace{3 cm}

{\large T\"ubingen\\
2017}\\

\vfill
\makeatother
\end{center}

>>>>

%\pagestyle{empty}
\begin{titlepage}
{

\makeatletter
\centering
% https://tex.stackexchange.com/a/241121/1340
\linespread{1.5}\selectfont
\parskip 0pt
%\sffamily

\vspace*{-2cm}

{\huge \bfseries
  \@title\par}

\vspace{4cm}
\large

{\bfseries Dissertation}\\
%
%\vspace{0.5cm}
%
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)

\vspace{4 cm}

vorgelegt von \\
\@author \\
aus Catania (Italien)

\vspace{2 cm}

T\"ubingen\\
2017

\vfill
\makeatother
}
\end{titlepage}
% TODO: insert here page 2 with the needed thesis boilerplate.
%\clearpage
% \pagestyle{myheadings}
